Article Title

### 2013-10-01 sections/Figure3.tex
updated estimator descriptions.
put all figures and sections in place.

\subsection*{Simulation}
To illustrate

\begin{figure}[htp]
\centering
\includegraphics[width=1.0\textwidth]{figures/Figure3.pdf}
\caption{
%\textbf{Figure 3.}{
Simulation results.
\textbf{A--D}: True $60\times60$ covariance matrices used in models. \textbf{A} does not have a low-dimensional structure.  \textbf{B} is a factor model with 8 factors. \textbf{C}
}\label{fig:03}
%}
\end{figure}

>>>>

\begin{figure}[htp]
\centering
\includegraphics[width=1.0\textwidth]{figures/Figure3.pdf}
\caption{
In simulation, selection amongst estimators recognizes the true covariance atructure. 
{\bf A--D} are examples of true $100\times100$ covariance matrices of multivariate normal distributions used in simulations. Matrix A has no low-dimensional structure. Matrices B--D have low-dimensional structture corresponding to the respective graphical models in Fig.~2B--D.
{\bf E--H} are examples of sample covariance matrices obtained from samples of size $n=1000$ from distributions with respective true covariance matrices A--D.
{\bf I--L:} Performance evaluation of covariance estimators A, B, C, D from samples obtained from models A, B, C, D.  Excess loss $\loss{\hat\Sigma,\Sigma}-\loss{\Sigma,\Sigma}$ is only accessible with the true covariance matrix $\Sigma$ is known and zero excess loss implies absolutely correct estimation. Estimators that can represent the graphical model outperform those that cannot.  Error bars indicate the standard deviation. 
{\bf M--P:} Performance evaluation using cross-validated \emph{empirical loss} from Eq.~\ref{eq:empiricalLoss} without knowledge of true $\Sigma$. Cross-validation reproduces the same relationship between performances of the estimators.
}\label{fig:03}
\end{figure}

### 2013-10-01 sections/Figure5.tex
put all figures and sections in place.

\begin{figure}[htp]
\centering
\includegraphics[width=0.5\textwidth]{figures/Figure2.pdf}
\caption{
Graphical models corresponding to the low-dimensional targets of the four regularization schemes used in the paper.
\textbf{A}: A diagonal matrix corresponds to a Gaussian graphical model with no dependencies.
\textbf{B}: In factor analysis, observed nodes are assumed to be influenced by several latent units (``factors") but are otherwise independent.
\textbf{C}: In the Gaussian graphical model (also known as the Gaussian Markov Field), correlations arise from sparse pairwise linear interactions between visible units.
\textbf{D}: In the Gaussian graphical model with latent units, correlations arise  between pairs of nodes
}\label{fig:02}
\end{figure}

>>>>

\begin{figure}[htp]
\centering
\includegraphics[width=1.0\textwidth]{figures/Figure5.pdf}
\caption{
Example of covariance structure revealed by the sparse+low-rank estimator and its relationship to the circuit arcitecture.
}
\label{fig:05}
\end{figure}

### 2013-10-01 sections/Findings.tex
put all figures and sections in place.

\subsection*{In visual cortex, Estimator D dominates}
\input{sections/Figure4.tex}
This is the full matrix of all comparisons of the estimators.  The plots represents the histograms of the differences of the loss function between the pair of estimators for all 31 sites.  When the differences are positive, the first estimate in the title outperforms the second estimate.

>>>>

\subsection*{In visual cortex, Estimator D dominates}
\input{sections/Figure4.tex}
Figure \ref{fig:04} showthe full matrix of all comparisons of the estimators.  The plots represents the histograms of the differences of the empirical loss between the pair of estimators for all 31 recorded sites.  When the differences are positive, the first estimate in the title outperforms the second estimate.

### 2013-10-01 sections/Simulation.tex
minor
expanded the section on covariance estimators
included figure5.
redistributed text between files, cleaned up text files.
put all figures and sections in place.

To illustrate

\begin{figure}
\centering
\includegraphics[width=1.0\textwidth]{figures/Figure3.pdf}
\caption{
%\textbf{Figure 3.}{
Simulation results.
\textbf{A}: A diagonal matrix corresponds to a Gaussian graphical model with no dependencies. 
}\label{fig:03}
%}
\end{figure}

>>>>

\subsection*{In simulation, estimator selection `recognizes' the covariance structure}
\input{sections/Figure3.tex}

Sample covariance matrices such as E,F,G,H are computed from samples of 1000 independent observations from multivariate normal distributions with true covariance matrices in A,B,C,D, respectively.  However, the true covariance matrices have various low-dimensional structures.

True matrix A has no low-dimensional structure.  It is computed as the sample covariance matrix of a finite sample (n=1000) of a multivariate Gaussian with independent identically distributed nodes.

True matrix B is computed by factor analysis of true matrix A with six factors.

True matrix C is computed by reducing to zero a large fraction the coefficients of the inverse of true matrix A.

True matrix D is computed by representing the inverse of true matrix A as the sum of a sparse component and a low-low rank component.

When we estimate the true covariance matrix from the samples of various sizes, we find that for true covariance matrices that have a low-dimensional structure, the covariance estimator whose target has the same type of low-dimensional structure attains lower loss. Plots I,J,K,L show the excess loss, which equals zero when the estimate equals truth (requires knowledge of truth). Plots M,N,O,P show empirical loss computed by cross-validation.  Empirical loss does not require knowledge of truth but is also shifted so that its absolute value is not particularity meaningful but it can be used for comparison. The error bars in these plots indicate the standard deviation, not standard error.

The loss function here is the multivariate log likelihood just as used in the previous post on real data.

The fact that estimate D outperformed the other estimates can be interpreted that the low-dimensional structure of the covariance matrices obtained from dense microcircuits in the visual cortex is best represented by the sparse+low-rank inverse model.

We can be then justified to examine the optimal fitted model rather than the sample covariance model in the analysis of neural correlations.  The sparse component represents the graph of interactions in the model, which we can now relate to the circuit architecture.  The low-rank component can be interpreted as common input into the circuit whose properties can be studied separately.

In this way, the process of selecting the best of several regularized covariance estimators serves as the method for recognizing the low-dimensional structure of covariance matrices in a specific domain.

Note that estimator D performs well on both purely sparse and purely low-rank models. But it does not do better.  Only when the truth is sparse+lowrank does it outperform the other estimates.
